Mirror, mirror on the wall. Who's the best match of them all?

### 2023-11-22 PNAS/index.Rnw
Fix first page
out with the wrong bib file

\firstpage[3]{8}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

Here, we consider the multiple comparisons problem that arises from a relatively simple toolmark comparison: matching a cut wire to a wire-cutting tool. We describe the approach and calculate the number of comparisons performed, and then assess the likelihood of a false positive error considering the multiple comparisons performed, using error rates derived from published black-box studies.

>>>>

\firstpage[3]{12}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

Here, we consider the multiple comparisons problem that arises from a relatively simple toolmark comparison: matching a cut wire to a wire-cutting tool. We describe the comparison approach, estimate the (minimal) number of comparisons needed, and discuss how the false discovery rate changes with the number of comparisons involved, using error rates derived from published black-box studies.
